\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-24 paper/main.tex
Explained why specific bugs were selected and why other issues/bugs are not reproducible, shortened code snippet for space

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard bugs that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we assess the reproducibility of the bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug.  Once we can successfully reproduce the bug by
creating the enviroment detailed in the report, we include the
corresponding artifacts in our dataset. Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> run-tool --container freefuzz --library-name pytorch \ 
   --use-library-version 2.2.0 \
   --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 120903 for library pytorch version 2.2.0
...
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
...
RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please report a bug to PyTorch.
====== 1 passed in 1.09s ======
...
Updating environment in the container of the testing tool
Successfully copied 16.4kB to freefuzz:/tmp/issue_120903
...
Running the testing tool on the environment of the bug
APIs under test:
torch.fake_quantize_per_channel_affine
torch.all
torch.compile
Testing on  ['torch']
torch.atanh
...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.fake_quantize_per_channel_affine did not face any failures
-> torch.all did not face any failures
-> torch.compile did not face any failures
Reproduced 0 out of 3 bugs
\end{lstlisting}

>>>>

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard bugs that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we do a deeper analysis on these bugs. We find some bugs that
are related to building/installation/problematic unit tests instead of
bugs in the core API functionality, as well as some bugs that lack any
code snippet provided with the bug report to reproduce the bug. These
bugs can be detected and discarded at this stage.
We assess the reproducibility of a bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
or can not be reproduced due to an expired nightly build that can no
longer be accessed. We successfully reproduce the bug if none of these
issues are present by
creating the enviroment detailed in the report, and we include the
corresponding artifacts in our dataset. Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> run-tool -c freefuzz -l pytorch -v 2.2.0 \
   --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:
\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 120903 for library pytorch version 2.2.0
...
RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
report a bug to PyTorch.
====== 1 passed in 1.09s ======
Updating environment in the container of the testing tool
...
Running the testing tool on the environment of the bug
APIs under test:
torch.fake_quantize_per_channel_affine
torch.all
torch.compile
Testing on  ['torch']
torch.atanh
...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.fake_quantize_per_channel_affine did not face any failures
-> torch.all did not face any failures
-> torch.compile did not face any failures
Reproduced 0 out of 3 bugs
\end{lstlisting}
